\documentclass[10pt,a4paper]{letter}
\usepackage[utf8x]{inputenc}
\usepackage{ucs}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\signature{Nathan Hugh Barr}
\address{Nathan Hugh Barr \\ Lysalleen 60 \\ 4000 Roskilde \\ Danmark}
\begin{document}

\begin{letter}{}
\opening{To whom it may concern:}

With my background in Mathematics and Physics I see myself as a potential candidate that can strengthen your analysis team. I am well versed in mathematical models and implementation of models in computer based analysis. What I can bring to the table is my ability to work within a team environment on the development of new predictive models using my theoretical mathematical foundation and my model building skills. I can contribute with new inputs and ideas which will have a positive outcome in the development process.

Projects that I have worked on through my education have been tackled using mathematical modelling, data analysis using statistical techniques and implementation in numerical based programming languages. I would like to give you an overview of some of the models I have worked with. I have build mathematical models from ground up to describe how oxygen both diffuses through white wine and packed meat. These have been based upon second order partial differential equations, which I have both tackled analytically and numerically. In these projects I have had to think outside the box as the objects that I modeled do not lie in the mathematical domain. In my master thesis, I took a simple model of how light transmits and reflects off a semi-transparent interface and developed this model to represent a multi-layer polymer upon a silicon wafer. 

I have experience with developing models within an environment which is unfamiliar to me and I am able to obtain results. I believe that I can contribute my ability to begin on a project with ease and my ability to build mathematical models. 

What drives me and my passion for data analysis is that data can be turned into insight. I believe that I have the knowledge and patience to extract key information from computer based results.      

I view myself as a cheerful and optimist person who is looking for new challenges.

I have attached a copy of my CV and a transcript of my bachelor and master's degree. I look forward to hearing from you about this position.   

\closing{Sincerely,}

\end{letter}

%I feel that I am fit for the position due to the following points. Physics as a discipline is based on a strong theoretical fundament and the ability to solve problems and I have this competence. I have an analytical competence through studying mathematics.
\end{document}