\documentclass[10pt,a4paper]{letter}
\usepackage[utf8x]{inputenc}
\usepackage{ucs}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\signature{Nathan Hugh Barr}
\address{Nathan Hugh Barr \\ Lysalleen 60 \\ 4000 Roskilde \\ Danmark}
\begin{document}

\begin{letter}{}
\opening{Dear Dorthe Gregersen:}

I writing to enquire about a visit to Rockwool, and work placement to gain workforce experience. I completed my Master's degree in Physics and Mathematics on the 7th of May and most of my work experience has been in academia and teaching. I would like to experience the day to day life of working in an international company and what types of jobs are completed over the course of the week. I am looking for experience in the IT department working with data and modelling data. I have experience with the programming languages Matlab and Python. I am also looking for experience in any research department. I have experience with different forms of light scattering which is used to investigate structural characterisation of materials. The skills that i have are in programming, mathematical modelling and experimental research.  

I view myself as a cheerful and optimist person who enjoys working in a team environment. I am a motivated and stable worker who is looking for new challenges. I look forward to hearing from you.

\closing{Sincerely,}

\end{letter}

%I feel that I am fit for the position due to the following points. Physics as a discipline is based on a strong theoretical fundament and the ability to solve problems and I have this competence. I have an analytical competence through studying mathematics.
\end{document}