\documentclass[10pt,a4paper]{letter}
\usepackage[utf8x]{inputenc}
\usepackage{ucs}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\signature{Nathan Hugh Barr}
\address{Nathan Hugh Barr \\ Lysalleen 60 \\ 4000 Roskilde \\ Danmark}
\begin{document}

\begin{letter}{EY \\ Osvald Helmuths Vej 4 \\ 2000 Frederiksberg}
\opening{Dear Sir or Madam :}

I writing to apply for the graduate position in Data and Analytics. I completed my Master's degree in Physics and Mathematics on the 7th of May and this position has taken my interest. I am interested in the emerging field of data analytics and machine learning and how these can be implemented in real world situations. I feel that I am fit for the position due to the following points. Physics as a discipline is based on a strong theoretical fundament and the ability to solve problems and I have this competence. I have an analytical competence through studying mathematics. During my tertiary education at Roskilde University, I have gained the ability to adapt to new projects outside my expertise quickly and I am comfortable and prefer to work in a team environment. I am a motivated, stable worker who is looking for new challenges and I feel that I can contribute to your company using my unique degree in Physics and Mathematics. 

I have attached a copy of my CV and a transcript of my bachelor and master's degree. I look forward to hearing from you about this position.   

\closing{Sincerely,}

\end{letter}


\end{document}