\documentclass[12pt,a4paper]{letter}
\usepackage[utf8x]{inputenc}
\usepackage{ucs}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[margin=0.5in]{geometry}
\signature{Nathan Hugh Barr}
\address{Nathan Hugh Barr \\ Østerbrogade 202 4.tv \\ 2100 København \\ Danmark \\ Tlf Nr: 61 73 55 92}
\begin{document}

\begin{letter}{}
\opening{\textbf{Cover Letter: Mathematics teacher in the IB Diploma Programme}} 

I am a newly graduated Cand.Scient in Physics and Mathematics who has a passion for teaching and the didactics of teaching mathematics. What I find fun when teaching mathematics is conveying complex mathematical ideas and concepts into easy and understandable ideas and concepts. I find teaching mathematics like solving a puzzle, there maybe a concept that a student is having difficulty with, and it is my job to assess and guide the student to the solution.

Though my multidisciplinary education I have experience with how mathematics is used in the other science disciplines. In my bachelor project I investigated how mathematical competencies in mathematics education (KOM Rapporten - M.Niss and T.H. Jensen) have evolved through danish high school education from $1958$ to the present using integral theory as a case study.

My teaching experience has come from being a teachers assistant for two introduction courses at Roskilde University and from being a private tutor in mathematics and physics through the company My Academy. In both jobs I have taught and assisted the students in their learning. I was also one of the founding members of the Roskilde Science Show where we developed at $45$ minute science show, showcasing projects and concepts in natural science.

To conclude I would like to give you an overview of who I am as an employee. My native language is English and my second language is Danish. I am an ambitious and optimist person who is all ready to help out when needed.

I look forward hearing from you about this position.

\closing{Sincerely,}
\end{letter}


\end{document}