\documentclass[10pt,a4paper]{letter}
\usepackage[utf8x]{inputenc}
\usepackage{ucs}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\signature{Nathan Hugh Barr}
\address{Nathan Hugh Barr \\ Lysalleen 60 \\ 4000 Roskilde \\ Danmark}
\begin{document}

\begin{letter}{}
\opening{To whom it may concern:}

I writing to enquire about work placement at Siemens to gain workforce experience. I would like to experience the workload and flow of projects. I would like to experience how projects are started, and how the projects are tackled throughout a work day and throughout the weeks. I am looking for experience in the IT department working with data analysis and modelling of data. I have experience with the programming languages Matlab and Python. I have experience in data analysis, taking data and turning it into insight. 

I am also looking for experience in any research department. I have experience with different forms of light scattering which is used to investigate structural characterisation of materials.

I view myself as a cheerful and optimist person who enjoys working in a team environment. I am a motivated and stable worker who is looking for new challenges. 

I look forward to hearing about current projects being worked on and how I can help contribute to these projects.

\closing{Sincerely,}

\end{letter}

%I feel that I am fit for the position due to the following points. Physics as a discipline is based on a strong theoretical fundament and the ability to solve problems and I have this competence. I have an analytical competence through studying mathematics.
\end{document}