\documentclass[10pt,a4paper]{letter}
\usepackage[utf8x]{inputenc}
\usepackage{ucs}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\signature{Nathan Hugh Barr}
\address{Nathan Hugh Barr \\ Østerbrogade 202 4.tv \\ 2100 København \\ Danmark}
\begin{document}

\begin{letter}{}
\opening{To whom it may concern:}

I am writing to express my interest in the data scientist position at Novo Nordisk. I am a newly graduated Cand.Scient in Physics and Mathematics with a broad skill-set. My education has revolved around mathematical modelling, mathematical theory and data processing using Matlab and Python.       
 
I have academic experience in scripting in Matlab and Python performing data analysis and model fitting. I have worked with a variety of datasets and models, both statistical and differential, and I have good visualisation skills in the programming languages stated above. My drive as a data scientist is the process of turning data into insight. I enjoy looking at data from different angles and I am able to communicate results to different audiences. 

I can see that I do not meet each requirement that was posted in this position, but I am positive that I can learn on the job due to my strong foundation in mathematics and programming.  

I am currently exploring machine learning and how to implement the machine learning algorithms in Python. I enjoy learning the inner workings of the mathematical models and algorithms used in machine learning, focusing on their strengths and weaknesses.  

I have excellent communication skills in both English and Danish. I am able to work both independently and within a team environment. I view myself as a cheerful and optimistic person who is not shy when met with new challenges and responsibilities.

I look forward to hearing from you about this position.   

\closing{Sincerely,}

\end{letter}


\end{document}