\documentclass[10pt,a4paper]{letter}
\usepackage[utf8x]{inputenc}
\usepackage{ucs}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\signature{Nathan Hugh Barr}
\address{Nathan Hugh Barr \\ Østerbrogade 202. tv \\ 2100 København Ø \\ Danmark}
\begin{document}

\begin{letter}{}
\opening{Dear Søren Bæk:}

I am writing to express my interest in the data scientist position in the Data Analytical Centre at the Danish Medicinal Agency. As you could probably see in my CV, I am a newly graduated Cand.Scient in Physics and Mathematics. Though the job advertisement calls for a minimum of 2 years employment in a relevant position, I believe my education has armed me with exactly what this position requires.

My education has revolved around the trinity of mathematical models, data processing and mathematical theory. I am confident in data extraction and data analysis using mathematical models and statistics. Through project work at Roskilde University, I have been trained in data ethics and unbiased data presentation. I was credited in my master thesis for the thorough presention of my results and of my good documentation of the experiments and procedures used. I am proficient in both python and matlab, and I believe I have a strong enough programming foundation to easily pickup any other programming languages, if need be. When programming, I take time to document my codes making them legible.

I have begun exploring machine learning and the learning algorithms commonly used in machine learning. I can contribute this to the evolution the Data Analytical Centre.  

I have excellent communication skills in both English and Danish, and I thrive in a team environment. I view myself as a cheerful and optimist person who is looking for new challenges.     

I look forward to hearing from you about this position.  

\closing{Sincerely,}

\end{letter}

 
\end{document}