\documentclass[10pt,a4paper]{letter}
\usepackage[utf8x]{inputenc}
\usepackage{ucs}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\signature{Nathan Hugh Barr}
\address{Nathan Hugh Barr \\ Lysalleen 60 \\ 4000 Roskilde \\ Danmark}
\begin{document}

\begin{letter}{}
\opening{Dear Søren Skytte:}

With my background in Mathematics and Physics I see myself as a potential candidate that can strengthen your analysis team. I am well versed in mathematical models and implementation of models in computer based analysis. What I can bring to the table is my ability to work within a team environment on the development of new predictive models using my theoretical mathematical fundament and my model building skills. I can contribute with new inputs and ideas which will have a positive outcome in the development process.

Projects that I have worked on through my education have been tackled using mathematical modelling, data analysis using statistical techniques and implementation in numerical based programming languages. I have build mathematical models from ground up to describe how oxygen both diffuses through white wine and packed meat. There I have had to think outside the box as the objects that I modelled do not lie in the mathematical domain. In my master thesis, I took a simple model of how light transmits and reflects off a semi-transparent interface and developed this model to represent a multilayer polymer upon a silicon wafer. I have experience with developing models within an environment which is unfamiliar to me and being able to obtain results. 

What drives me and my passion for data analysis is the thought that the end product can help drive decisions and in the end, help people. I believe that I have the knowledge and patience to extract key information from computer based results.      

I view myself as a cheerful and optimist person who is looking for new challenges.

I have attached a copy of my CV and a transcript of my bachelor and master's degree. I look forward to hearing from you about this position.   

\closing{Sincerely,}

\end{letter}

%I feel that I am fit for the position due to the following points. Physics as a discipline is based on a strong theoretical fundament and the ability to solve problems and I have this competence. I have an analytical competence through studying mathematics.
\end{document}