\documentclass[10pt,a4paper]{letter}
\usepackage[utf8x]{inputenc}
\usepackage{ucs}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\signature{Nathan Hugh Barr}
\address{Nathan Hugh Barr \\ Østerbrogade 202 4.tv \\ 2100 København \\ Danmark}
\begin{document}

\begin{letter}{}
\opening{To whom it may concern:}

I am writing to express my interest in the Senior Statistical Programmer for Clinical Development position. The position sounds very interesting, I can see myself working with complex data from different sources, compiling and merging data to a complete data set and handing the torch over to the bio-statisticians.

My background is interdisciplinary mathematics and physics and I am a self taught python programmer who has the ability to write efficient and well documented scripts and programs. I am a member of two research groups that implement python programming to control educational robots from a danish company called Shape robotics and analyse large data sets using machine learning. This has given me a deep understanding of python, importing data, data handling and data visualisation. From my mathematical background I am competent in the analysis of data and the formulation of conclusions. In these two research groups I collaborate with teachers from different subjects, who also come from different academic backgrounds. From my job as a gymnasium teacher I have learnt how to think on my feet, how to plan multiple class at different levels with different needs. I have had two years experience in teaching where I have trained my communication skills both oral and written. I can juggle projects, emails and deadlines simultaneous and I am always open for sparing. I can take on responsibility and I take the initiative when I can see that it will help the team meet it's goals.             

%I view myself as a cheerful and optimistic person who is not shy when met with new challenges and responsibilities.

I look forward to hearing from you about this position and you are more than welcome to keep my personal information for a different position within the bio-statistics team.   

\closing{Sincerely,}

\end{letter}


\end{document}