\documentclass[10pt,a4paper]{letter}
\usepackage[utf8x]{inputenc}
\usepackage{ucs}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\signature{Nathan Hugh Barr}
\address{Nathan Hugh Barr \\ Lysalleen 60 \\ 4000 Roskilde \\ Danmark}
\begin{document}

\begin{letter}{}
\opening{Dear Tony Shepherd:}

I writing to apply for the Future Data Scientist position. I completed my Master's degree in Physics and Mathematics on the 7th of May and this position has taken my interest. I am interested in the emerging field of data analytics and how this can be implemented in real world situations. Most of my written projects during my tertiary education have revolved around the analysis of data using statistical techniques and comparison to mathematical models. I feel I have a strong grasp on statistical analysis and I will have no problem quickly immersing myself in the position of providing relevant analysis of data sets. I am currently learning how to program in python, I feel that this is going smooth due to me having worked with the program called Matlab throughout my education. My master's degree in Physics and Mathematics is quiet broad and I consider myself as a generalist. I believe that this can benefit your team as I have the ability to quickly create an overview when moving into new projects. I was a member of the Roskilde University Scienceshow and from that job I have gained the ability to formulate and communicate complex idea's and concept's to different groups of people without losing the essence of what I am trying to convey.  I view myself as a cheerful and optimist person who enjoys working in a team environment. I am a motivated and stable worker who is looking for new challenges. I feel that I can contribute to your team using my unique degree in Physics and Mathematics and my ability to quickly immerse myself in new projects. 

I have attached a copy of my CV and a transcript of my bachelor and master's degree. I look forward to hearing from you about this position.   

\closing{Sincerely,}

\end{letter}

%I feel that I am fit for the position due to the following points. Physics as a discipline is based on a strong theoretical fundament and the ability to solve problems and I have this competence. I have an analytical competence through studying mathematics.
\end{document}