\documentclass[10pt,a4paper]{letter}
\usepackage[utf8x]{inputenc}
\usepackage{ucs}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\signature{Nathan Hugh Barr}
\address{Nathan Hugh Barr \\ Lysalleen 60 \\ 4000 Roskilde \\ Danmark}
\begin{document}

\begin{letter}{}
\opening{To whom it may concern:}

With my background in Mathematics and Physics I see myself as a potential candidate that can strengthen your data scientist team. I am well versed in mathematical models and statistical based analysis. What I can bring to the table is my ability to work on turning data into insight using my theoretical mathematical foundation. I have experience working with large data-sets and I can write up reports containing visualisation and analysis of the data. I am proficient in Linux and Python and I have a strong foundation in scripting and programming which I believe can contribute to your data scientist team. I have not used the programming language R but I am positive that I can learn the language on the job.
 
I have excellent communication skills in both English and Danish, and I thrive in a team environment. It is stated in the job advertisement, that Block by Block is looking for a student. I don't classify for this requirement as I have completed my Cand.Scient in Physics and Mathematics, but I am looking for work experience. If there is a position that I can fill, I am interested in hearing about it.

I view myself as a cheerful and optimist person who is looking for new challenges.

I have attached a copy of my CV and a transcript of my bachelor and master's degree. I look forward to hearing from you about this position.   

\closing{Sincerely,}

\end{letter}

%I feel that I am fit for the position due to the following points. Physics as a discipline is based on a strong theoretical fundament and the ability to solve problems and I have this competence. I have an analytical competence through studying mathematics.
\end{document}