\documentclass[10pt,a4paper]{letter}
\usepackage[utf8x]{inputenc}
\usepackage{ucs}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\signature{Nathan Hugh Barr}
\address{Nathan Hugh Barr \\ Østerbrogade 202 4.tv \\ 2100 København \\ Danmark}
\begin{document}

\begin{letter}{}
\opening{To whom it may concern:}

With my background in Mathematics and Physics I see myself as a potential candidate that can strengthen your data scientist team. I am well versed in mathematical models and statistical based analysis. What I can bring to the table is my ability on turning data into insight using my theoretical mathematical foundation. I am proficient in python and I have a strong quantitative and analytical skillset in python. I have experience working with large data-sets and I writing reports containing visualisation and analysis of the data.  I have knowledge of SQL, Numpy, pandas and scikit-learn. My motivation for working with data analysis is the unique combination of theoretical mathematics and insight gained from a data-set.    
 
I have excellent communication skills in both English and Danish, and I am able to work both independently and within a team environment. I view myself as a cheerful and optimistic person who is looking for new challenges.

I have attached a copy of my CV and a transcript of my bachelor and master degree. I look forward to hearing from you about this position.   

\closing{Sincerely,}

\end{letter}

%I feel that I am fit for the position due to the following points. Physics as a discipline is based on a strong theoretical fundament and the ability to solve problems and I have this competence. I have an analytical competence through studying mathematics.
\end{document}