\documentclass[10pt,a4paper]{letter}
\usepackage[utf8x]{inputenc}
\usepackage{ucs}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\signature{Nathan Hugh Barr}
\address{Nathan Hugh Barr \\ Østerbrogade 202 4.tv \\ 2100 København \\ Danmark}
\begin{document}

\begin{letter}{}
\opening{Dear Peter Sinding:}

I am writing to express my interest in the data scientist position at Norden. I am a newly graduated Cand.Scient in Physic and Mathematics with a broad skill-set. My education has revolved around mathematical modelling, mathematical theory and data processing using Matlab and Python.       
 
Most of my projects in my higher education, have revolved around the building of mathematical models and the testing of them using data-sets and statistical analysis. I have the ability to clean and extract data from large data-sets and programming abilities to automate this process. I enjoy both starting on a new project and following it to its completion. 

I am currently exploring machine learning and how to implement the machine learning algorithms in Python. I enjoy learning the inner workings of mathematical models, focusing on their strengths and weaknesses.  

I have excellent communication skills in both English and Danish and I am able to communicate results to different types of audiences. I am able to work both independently and within a team environment. I view myself as a cheerful and optimistic person who is not shy when met with new challenges and responsibilities.

I look forward to hearing from you about this position.   

\closing{Sincerely,}

\end{letter}


\end{document}